### 2016-03-24 paper.tex
Remove TotAN board image to reduce page count to 7

\newcommand{\totan}{\textit{TotAN}}
\newcommand{\smersh}{\textit{SMERSH}}

@@

\textit{Tales of the Arabian Nights}~\citep{Goldberg2009} is a 
tabletop board game based on the eponymous folk tale,
originally published in 1985~\citep{Goldberg1985} and
released with many revisions in 2009.
It is popular among board game hobbyists, having a board game
rank of~239 (thematic rank~75) on Board Game Geek as of this writing,
and Shut Up \& Sit Down rank it as the ninth best game of all 
time~\citep{ShutUp2015}.
In this game, players control a character within a mythical Arabian
setting, exploring the known world to accumulate Story and
Destiny points. The winner is the one who is able to meet their 
Story and Destiny point goal while having a successful encounter
in Baghdad---the City of Peace. Notice in Figure~\ref{fig:totan-board}
that Baghdad is the center of the world, much larger and more beautiful
than any other city.

\newcommand{\figwidth}{2.5in}
%\begin{wrapfigure}{R}{\figwidth}
\begin{figure}[b]
\centering
\includegraphics[width=\figwidth]{totan-board}
\caption{Center of the \textit{Tales of the Arabian Nights} game board~\citep{Goldberg2009}.}
\label{fig:totan-board}
%\end{wrapfigure}
\end{figure}

@@

The other formal element excluded from the genre definition is the use of an
explicit map. The map is an important tangible aspect of \totan{}, 
in particular with its representation of Baghdad as the largest, most
important city in the world (Figure~\ref{fig:totan-board}). 
However, we also note that virtual spaces
can be represented without such an explicit map, such as in text adventures,
the MUD family of games, or choose-your-own-adventure books, both of which
use discrete spaces without giving them visual manifestation.

>>>>

\newcommand{\totan}{\textit{TotAN}}
\newcommand{\smersh}{\textit{SMERSH}}
\newcommand{\figwidth}{2.5in}

@@

\textit{Tales of the Arabian Nights}~\citep{Goldberg2009} is a 
tabletop board game based on the eponymous folk tale,
originally published in 1985~\citep{Goldberg1985} and
released with many revisions in 2009.
It is popular among board game hobbyists, having a board game
rank of~239 (thematic rank~75) on Board Game Geek as of this writing,
and Shut Up \& Sit Down rank it as the ninth best game of all 
time~\citep{ShutUp2015}.
In this game, players control a character within a mythical Arabian
setting, exploring the known world to accumulate Story and
Destiny points. The winner is the one who is able to meet their 
Story and Destiny point goal while having a successful encounter
in Baghdad---the City of Peace.

@@

The other formal element excluded from the genre definition is the use of an
explicit map. The map is an important tangible aspect of \totan{}, 
in particular with its representation of Baghdad as the largest, most
important city in the world. 
However, we also note that virtual spaces
can be represented without such an explicit map, such as in text adventures,
the MUD family of games, or choose-your-own-adventure books, both of which
use discrete spaces without giving them visual manifestation.
